%% start of file `template.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.
\documentclass[11pt,a4paper,sans]{moderncv}        % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')

% moderncv themes
\moderncvstyle{casual}                             % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{blue}                               % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
%\renewcommand{\familydefault}{\sfdefault}         % to set the default font; use '\sfdefault' for the default sans serif font, '\rmdefault' for the default roman one, or any tex font name
%\nopagenumbers{}                                  % uncomment to suppress automatic page numbering for CVs longer than one page

% character encoding
%\usepackage[utf8]{inputenc}                       % if you are not using xelatex ou lualatex, replace by the encoding you are using
%\usepackage{CJKutf8}                              % if you need to use CJK to typeset your resume in Chinese, Japanese or Korean

% adjust the page margins
\usepackage[scale=0.75]{geometry}
\usepackage{multicol}
%\setlength{\hintscolumnwidth}{3cm}                % if you want to change the width of the column with the dates
%\setlength{\makecvtitlenamewidth}{10cm}           % for the 'classic' style, if you want to force the width allocated to your name and avoid line breaks. be careful though, the length is normally calculated to avoid any overlap with your personal info; use this at your own typographical risks...

% personal data
\newcommand\colorhref[3][cyan]{\href{#2}{\small\color{#1}#3}}
\name{Ivan}{Malison}
\title{Software Engineer}
\address{747 Leavenworth Street}{94109 San Francisco, CA}{United States}
\phone[mobile]{+1~(301)213-6635}
\email{ivanmalison@gmail.com}
\social[linkedin]{ivan.malison}
\social[github]{IvanMalison}
\setlength{\hintscolumnwidth}{0.19\textwidth}
\begin{document}
\makecvtitle

\section{Education}
\cventry{2008--2012}{Bachelor of Mathematics}{Reed College}{Portland, Oregon}{}{}
\cventry{2004--2008}{High School}{The Field School}{Washington D.C.}{}{}

\section{Undergraduate Thesis}
\cvitem{title}{\emph{Graph Algorithms on Graphical Processing Units: The Shortest Path Problem}}
\cvitem{advisor}{James Fix}
\cvitem{description}{The GPU has shown great promise as a platform for general computation, but most of its successes have been with problems that are embarrassingly parallel. The objective of this thesis is to attempt the solution of a problem that exhibits more limited data-parallelism on the GPU. Specifically, it will examine the Shortest Path problem as it fits the aforementioned criteria and is an extremely important and well understood problem in Computer Science.}
\cvitem{link}{\colorhref{https://github.com/IvanMalison/Thesis/blob/master/thesis.pdf?raw=true}{Download PDF}{}}

\section{Experience}
\datedcventry{August 2012}{May 2014}{Software Engineer}{Yelp Inc.}{San Francisco, CA}{}{Served as a key member of Yelp's BAM/Partnerships team.
\begin{itemize}
\item Part of a 3 person subteam that built a system for large scale data exchange relationships with partners including eat24, delivery.com and many international data providers. The system had processsed tens of millions of jobs within a few months of its completion.
\item Pushmaster: Responsible for deploying new versions of the primary web applications for groups of as many as 20 other engineers on a bi-weekly basis. Also had service pushmaster privileges and performed service pushes for members of my team.
\item Refactored the method by which many extremely important internal metrics were calculated to reduce their run time by a factor of two. This involved 10+ tables and on the order of 100 million rows.
\item Became an expert with Yelp's gearman based asynchronous queing system (Yelp maintains the python gearman client). Contributed several bug fixes.
\item Was tasked with continuously monitored several of our teams most important systems. Fixed production systems on the weekend on numerous occassions.
\item Strong advocate for test driven development. Contributed several utilities to simplify the testing of distributed components of the Yelp service.
\item Led a large refactor of Yelp's datawarehouse system. Assisted with moving it from an in house MySQL cluster to Amazon Redshift.
\item Mentored and assisted interns with their projects.
\end{itemize}}
\datedcventry{September 2011}{May 2012}{Student Teaching Assistant}{Reed College}{Portland, OR}{}{
\begin{itemize}
\item Graded homework assignments for Calculus and Analysis courses for professors James Pommersheim and Rao Potluri.
\item Held tutor office hours once a week where students could come for assistance with coursework in 100 and 200 level math and computer science courses.
\end{itemize}
}
\datedcventry{June 2011}{August 2011}{Software Engineering Intern}{Action Systems Inc.}{Silver Spring, MD}{}{Assisted with the development of the iOS component of the write-on point of sale application. Added a new feature called groups mode to the application.}{}
\datedcventry{June 2010}{August 2010}{Quality Assurance Engineer}{Visual Solutions Inc.}{Westford, MA}{}{
Worked with full time engineers to test the VisSim graphical embedded development environment.}{}
\section{Programming Languages}
\subsection{Highly Proficient(10,000+ lines)}
\cvitem{Python}{Experience with both Python 2 (2.6 and 2.7) and Python 3. Some PyPy Experience, limited CPython C extension experience.}{}
\cvitem{Scala}{Strongest/Preferred JVM language. Prefer ensime/emacs to eclipse, but have some scala/eclipse experience.}
\cvitem{Java}{Familiar with java development in NetBeans and Eclipse.}
\cvitem{JavaScript}{Familiar with jQuery and several more modern MVC frameworks. Very familiar with angularjs.}
\cvitem{Shell}{Particularly familiar with zsh and bash. Some csh experience.}
\cvitem{C}{}

\subsection{Familiar}
\cvitem{Ruby}{Some Ruby on Rails experience.}
\cvitem{Lisp}{Most familiar with elisp. Also some experience with clojure.}
\cvitem{Objective-C}{Some iOS experience.}
\cvitem{C++}{}
\cvitem{Haskell}{}

\section{Technologies/Libraries/Tools}
\subsection{Highly Proficient}
\cvitem{unix}{Most comfortable with debian based linux and Mac OSX.}
\cvitem{emacs}{\colorhref{https://github.com/IvanMalison/.emacs.d}{My .emacs.d}}
\cvitem{sqlalchemy}{A Flexible python based ORM}
\cvitem{git}{}
\cvitem{mySQL}{}
\cvitem{angularjs}{}
\cvitem{\LaTeX}{}
\cvitem{Pyramid/Django/Tornado/Flask}{}

\subsection{Familiar}
\cvitem{Apache HTTP Server}{}
\cvitem{Akka}{}
\cvitem{backbonejs}{}
\cvitem{nginx}{}
\cvitem{OpenCL}{}
\cvitem{sbt}{}
\cvitem{Kafka}{}
\cvitem{mercurial}{}
\cvitem{postgresql}{}
\cvitem{Amazon EC2/S3}{}

\section{Recent Side Projects}

\cvitem{\colorhref{https://github.com/IvanMalison/chess_stats}{Chess Stats}}{Website to aggregate statistics and allow computer analysis of chess games played on chess.com. Python/Tornado/AngularJS}
\cvitem{\colorhref{https://github.com/att14/XPBoard}{XPBoard}}{A website that provides a virtual post by integrating data pulled from the Trac ticketing system and the ReviewBoard code review application. Python/Flask/AngularJS}
\cvitem{\colorhref{https://github.com/IvanMalison/Pool}{Pool}}{A 3D pool simulation with a physics engine written completely from scratch. Java/jMonkeyEngine 3.0}
\cvitem{\colorhref{https://github.com/stug/ray_caster}{Ray Caster}}{A rudimentary 2.5d engine. Python/Pygame}
\end{document}

